---
params:
  title: "50 years of hits: exploring the top 20 songs by artist (1960-2000)"  
  author: "Matt Malishev"
  social: "@darwinanddavis"    
  primary: "#5B3794"
  secondary: "#EFEFEF"
  imgdir: "plots"
  github: "https://github.com/darwinanddavis/misc/tree/gh-pages/celonis"      
output: 
  html_document:
    theme: "cosmo"
    css: css/style.css
    includes:
      in_header: header.html
      after_body: footer.html
---

<!-- css for tabs -->
<style type="text/css">

.nav>li>a{
    position: relative;
    display: block;
    padding: 10px 15px;
}

.nav-pills>li>a:hover{
  background: `r params$primary`;
  color: `r params$secondary`;
  opacity:0.7;
}

.nav-pills>li>a:focus, .nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus {
  background: `r params$primary`;
  background-color: `r params$primary`;
}

</style>

```{r, set-options, echo = F, cache = T, message=F}
options(width=25,tinytex.verbose = TRUE, width.cutoff=25)
knitr::opts_chunk$set(
 eval = F, # run all code
 echo = F, # show code chunks in output 
 tidy = T, # make output as tidy
 message = F,  # mask all messages
 warning = F, # mask all warnings 
 size="small", # set code chunk size,
 tidy.opts=list(width.cutoff=25) # set width of code chunks in output
)

# tinytex::install_tinytex()
# require(tinytex)
# install.packages("pacman")
# require(pacman)
```

# <span style="font-size: 200%;">`r params$title`</span> {.tabset .tabset-fade .tabset-pills}  

\  

<!-- tab break --------------------------------------------- -->
## Dashboard 1  

<span font-size: 1.5em;> 
<br>
  Ranking artist and song. Explore ranked data of artist based on energy, tempo, danceability, and liveness.  
  </span>   
```{r, eval=T, echo = F}
htmltools::includeHTML("index.html")
```


<!-- tab break --------------------------------------------- -->
## Dashboard 2

<span font-size: 1.5em;>
<br>
  Deep dive into data patterns. Find correlations between song energy and loudness/tempo linked to song rank, decade, and song/artist location.   
  <br>
  Use the slider to define rank, checkboxes to limit decade, and plots/map to select data windows (brush). The table at the bottom displays further info on the selected data for further snapshot comparisons.       
  </span>   
```{r, echo=F, warning=F}
# read data  
suppressWarnings(pacman::p_load(networkD3,dplyr,jsonlite,ggplot2,colorspace,readr,stringr,scales,d3scatter,crosstalk,leaflet,tibble,httpuv,DT,htmltools,geosphere,rnaturalearthdata,rnaturalearth,mapdata,sf))
fh <- "songs.json"
df <- jsonlite::fromJSON(fh)
```


```{r, echo=F, warning=F}
# create datasets 

require(geosphere)
require(leaflet)
require(rnaturalearthdata)
require(rnaturalearth)
require(maps)
require(sf)

# create crosstalk df
sd <- SharedData$new(df)

# map city data 
countries <- sd$data()[,"Country"] %>% unique 
cities <- sd$data()[,"City"] %>% unique

# get latlons for df$City
data(world.cities) # /maps
world_cities <- world.cities 
city_df <- world_cities %>% 
  dplyr::filter(country.etc %in% c(countries,"USA","UK"), 
                name %in% c(cities,"Goteborg")) %>% 
  # distinct(name, .keep_all = T) %>%
  dplyr::select(Y = lat,
                X = long,
                City = name, 
                Country = country.etc) %>% 
  left_join(sd$data(), by = "City", suffix=c(".x",".y")) %>%
  select(-ends_with(".x"),-ends_with(".y"))

city_df <- city_df[!duplicated(city_df[c("City","Country"),]),] # remove duplicates (inaccurate)  

# create new crosstalk df with latlon for df$City
sd2 <- SharedData$new(city_df)

```

```{r, echo=F, warning=F}
# map params 
var1 <- "Rank"
xlab <- "ENERGY"
colt <- "#5B3794"
colf <- "#F8DCD9"
colv <- colt
opac <- 0.9
ttl <- "Top 20 songs per city"
custom_tile <- "https://tiles.stadiamaps.com/tiles/alidade_smooth/{z}/{x}/{y}{r}.png"

setview <- c(0,0)

style <- list("color" = colv,"font-weight" = "normal","padding" = "8px")
text_label_opt <- labelOptions(noHide = F, direction = "top", textsize = "10px",
                               textOnly = F, opacity = 0.7, offset = c(0,0),
                               style = style, permanent = T
)

heading_tr <- paste0(
    "<span style=color:",colt,";> ",ttl," </span><br>",
    "Hover over locations for more info"
) 

popup_func <- function(d) paste0("<strong><span style=color:",colt,";>",d %>% pull(City),"</span></strong><br/><br/>",
                                 "<strong>","Artist: ","</strong><span>", d %>% pull(Artist),"</span><br/>",
                                 "<strong>","Song: ","</strong><span>", d %>% pull(Name),"</span><br/>",
                                 "<strong>","Decade: ","</strong><span>", d %>% pull(Decade),"'s</span><br/>",
                                 "<strong>",var1,": </strong><span>", d %>% pull(var1),"</span><br/>") %>% purrr::map(htmltools::HTML)

# easy buttons 
locate_me <- easyButton( # locate user
  icon="fa-crosshairs", title="Zoom to my position",
  onClick=JS("function(btn, map){ map.locate({setView: true}); }"));

reset_zoom <- easyButton( # reset zoom 
  icon="fa-globe", title="Reset zoom",
  onClick=JS("function(btn, map){ map.setZoom(3);}"));  

map_control_box <- htmltools::tags$style( 
  htmltools::HTML(".leaflet-control.layers-base { 
                  text-align: left;
                  padding-left: 10px; 
                  padding-right: 10px; 
                  background: white; opacity: 1;
                  font-size: 20px;
                  }"
       ))

control_box <- htmltools::tags$div(
  map_control_box, htmltools::HTML("")
)  

```

```{r, echo=F, warning=F}
# build crosstalk 

bscols(widths = c(12,6,6),
       list(
         filter_slider("rank", "Rank", sd2, ~Rank, step = 1, pre = "Rank "),
         filter_checkbox("Decade", "Decade", sd2, ~paste0(Decade,"'s"), inline = T)
       ),
       list(
         leaflet(sd2, width = "100%", height = 400) %>% 
           addTiles() %>%
           setView(setview[1],setview[2],zoom=1) %>% 
           addCircleMarkers(
             lng = sd2$data()[, "X"] %>% jitter(5),
             lat = sd2$data()[, "Y"] %>% jitter(5), 
             color = colt, fillColor = colt, radius = ~Rank, 
             opacity = opac, fill = T, stroke = T, weight = 1,
             popup = popup_func(sd2$data()),
             label = popup_func(sd2$data()), # paste(sd2$data()[,"City"]),
             labelOptions = text_label_opt, popupOptions = text_label_opt
           ) %>% 
           addProviderTiles("Stamen.TonerLite") %>%
           addControl(heading_tr,"topright") %>%
           addEasyButton(reset_zoom)
       ),
       list(
         d3scatter(sd2, ~energy, ~loudness, color = ~Rank, width = "100%", height = 200,x_label = xlab, y_label = "LOUDNESS"),
         d3scatter(sd2, ~energy, ~tempo, color = ~Rank,width = "100%", height = 200,x_label = xlab, y_label = "TEMPO")
       ),
       list(
         datatable(sd2, rownames = F,autoHideNavigation = T, fillContainer = F,
                   class="compact", extensions="Scroller",
                   options=list(deferRender=T, scrollY = 200, scrollX = 100, scroller=T,
                                pageLength = 5, autoWidth = T),
                   style = "bootstrap",
                   width = "100%", height = 200)
       )
)

```

